\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-02-08 chapters/3_algorithm.tex
Add first version of new alg. and binary tree formulation

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e. $(S_u \times S_v) \cap E$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.

@@

\begin{algorithm}[t]
  \begin{flushleft}
  \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
  \footnotesize
  % \small
      \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
      \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
      \Repeat
        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$
          \State Update interactions \& constraints with neighboring clusters
        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
          \State Add CannotLink Constraint between $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
      \State
      \Return $\Pi$
  \end{algorithmic}
    \label{main_alg}
  \end{flushleft}

@@

\begin{figure}
\centering
        \begin{subfigure}[t]{0.42 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \\\vspace{8pt}
    \begin{subfigure}[t]{0.42 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. The edge selected at each iteration is highlighted in yellow. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}

% \begin{table*}[t]
%     % \centering
%     \scriptsize
%     \begin{subtable}[t!]{0.6\textwidth}\centering
%         \begin{tabular}{r  l | c | c  c}
%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

@@

%         \end{tabular}
%     \end{subtable} 
%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
%     \label{tab:linkage-criteria}
% \end{table*}

@@

            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Average Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Complete Linkage\\Hier. Aggl. Clust.} \\
            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule

@@

\begin{figure*}
\centering
\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

>>>>

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$. \TODO{remove and add multicut energy, define HC}

\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. Let the interaction $\interact(S_u,S_v)$ between the two clusters be defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, \TODO{Remove $\Pi$ from def. Problem of zero interactions} named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e. $(S_u \times S_v) \cap E$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.

\textbf{Hierarchical trees} In HC literature, a \emph{dendrogram} $T$ is a rooted binary tree\footnote{In general, one could look at trees that are not binary. However, the algorithms discussed in this paper always generate binary hierarchical trees, so nothing would be gained by this generalization.} whose leaves are in one-to-one correspondence with $V$, representing the merging order of an agglomerative algorithm.
Let $T_{\mathrm{R}},T_{\mathrm{L}}\subset T$ denote the subtrees rooted at the two children of the root node in $T$.
For any two leaves $u,v \in V$, let $T[u \vee v]$ be the subtree rooted at the least common ancestor of $u$ and $v$ (furthest from the root), and let \texttt{leaves}$(T[u \vee v])\subseteq V$ be the set of leaves of this subtree. 
\TODO{Here we talk about the algorithm already, so we could move it to next section and the flow could be better. But we need a tree in the alg. So we better do this later}
For each pairs of leaves $u,v$, we can then assign a \emph{height} to their least common ancestor in the tree $T^*$ corresponding to the linkage/interaction between clusters $S_u$ and $S_v$ when $u$ and $v$ were merged by the algorithm:
% Then, given a binary tree $T$ and a linkage criterion $\interact$, we can associate a \emph{signed similarity} function $\treeHeight$ to each pair of distinct original nodes $u\neq v$, with $u, v \in V$:
\begin{equation}
\treeHeight(u,v) \equiv \interact{} \big( \text{\texttt{leaves}}(T_{\mathrm{R}}[u \vee v]), \text{\texttt{leaves}}(T_{\mathrm{L}}[u \vee v]) \big)
\end{equation}

\textbf{Ultrametrics}  Let us define the function $d_T: V \times V \rightarrow \mathbb{R}^{+}$ as:
\begin{align}
d_T(u,v)\equiv &\begin{cases}
0 & \text{if}\,\, u=v\\
M-\treeHeight(u,v) & \text{if}\,\, u\neq v
\end{cases}\quad \forall u,v\in V\\
\mathrm{where}& \quad  M \equiv \max_{u',v'\in V,\,u'\neq v'}\treeHeight(u',v').
\end{align}
In the next section, we will show that for some specific choices of linkage $\interact{}$, then $(V, d_{T^*})$ is an ultrametric on the original graph, where $T^*$ is the hierarchical tree built by the \algname{} algorithm.

\begin{itemize}
\item Def: A metric space $(X,d)$ is an \emph{ultrametric} if for every $x,y,z \in X$, $d(x,y)\leq \max \{d(x,z), d(y,z)\}$.
\item The connection between hierarchical trees and ultrametrics is well known. Normally, ultrametrics are associated to strictly positive \emph{similarity} or \emph{dissimilarity} measures on a graph. In our case, the interaction $\treeHeight{}$ can also be negative, so we first map these interactions to strictly positive values:

\item By definition, we have that $d_T(u,v)\geq 0$, $d_T(u,v)=d_T(v,u)$, and $d_T(u,u)= 0$. So, to prove that $(V, d_{T^*})$ is an ultrametric, we need to prove that
\begin{equation}
\interact{}_{T^*}(u,v) \geq \min \{\interact{}_{T^*}(u,t), \interact{}_{T^*}(v,t)\}
\end{equation}
 $\forall u,v,t\in V$. In other words, we want to make sure that, at every iteration, the algorithm merges pairs of clusters with lower and lower interactions. 
\begin{equation}
\interact{}_{T^*}(u,v) \geq \interact{}_{T^*}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
\end{equation}
This does not happen for all linkages (see Sum fig. 1) and when constraints are in place.  
 % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
\item We call a linkage invariant to $\alpha$-shift of weights, if by changing all edge weights of the graphs by a constant $w_e+\alpha$ the structure of the hierarchical tree  does not change and defines the same function $d_T$. (And correlation clustering problem is not like that).
\end{itemize}

@@

\begin{algorithm}[t]
\footnotesize
  \begin{flushleft}
  \footnotesize
  \caption{\algname{}}
  % \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; \\ 
   \hspace*{4.3em}boolean {\color{blue}addCannotLinkConstraints}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi^*$, rooted binary hierarchical tree $T^*$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
  \footnotesize
  % \small
      \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
      \State Initialize hierarchical tree $T$ with leaves nodes $V=\{v_1,\ldots,v_{|V|}\}$
      \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
      \State \emph{// Phase 1: Merge positive interactions (possibly using constraints)}
      \State Push absolute interactions $|w_e|$ to priority queue $PQ$
      \Repeat 
        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $|\interact{}(S_u,S_v)|$
        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
          \State Update interactions \& constraints with neighboring clusters
        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
          \State Add CannotLink Constraint between $S_u$ and $S_v$
        \EndIf
      \Until{\big[$PQ$ is empty\big]}
      % \State
      % \If{{\color{blue}addCannotLinkConstr}} % \Comment{Step 2: release constraints}
      \State \emph{// Phase 2: Relax constraints \& merge remaining positive interactions}
      \State Push signed interactions $\interact{}(S_u,S_v)$ to PQ, $\forall S_u, S_v \in \Pi$
      \Repeat 
        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
        \If{\big[{\color{green}\textbf{$\interact{}(S_u,S_v) > 0$}}\big]}
          \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
          \State Update interactions with neighboring clusters
        \EndIf
      \Until{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]} 
      \State Save the final clustering $\Pi^* \gets \Pi$ 
      \State \emph{// Phase 3: Merge negative interactions until one single cluster is left}
      \Repeat
        \State Pop $S_u,S_v\in\Pi$ from $PQ$ with highest interaction $\interact{}(S_u,S_v)$
        \State Merge clusters $S_u$, $S_v$ and update hierarchical tree $T$
        \State Update interactions with neighboring clusters
      \Until{\big[Only one cluster is left in $\Pi$\big]} 
      % \EndIf
      \State
      \Return $\Pi^*$, $T^*\gets T$
  \end{algorithmic}
    \label{main_alg}
  \end{flushleft}

@@

\begin{figure}[t]
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill \vspace{8pt}
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. The edge selected at each iteration is highlighted in yellow. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}

% \begin{table*}[t]
%     % \centering
%     \scriptsize
%     \begin{subtable}[t!]{\textwidth}\centering
%         \begin{tabular}{R{5em}  l | M{10em} | M{8em}  M{8em}}
%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria}\\ $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned} \\\textbf{Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No \\Constraints}} & \thead{With\\ Constraints} \\

@@

%             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
%         \end{tabular}
%     \end{subtable} 
%     \vspace{1em}
%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
%     \label{tab:linkage-criteria}
% \end{table*}

@@

            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Average Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Complete Linkage\\Hier. Aggl. Clust.} \\
            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{Average Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Complete Linkage\\Hier. Aggl. Clust.} \\
            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{\textbf{NEW}} % \thead{Greedy Fixation \cite{levinkov2017comparative}} 
            & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

### 2021-02-08 chapters/5_experiments_spectral.tex
Add first version of new alg. and binary tree formulation

\begin{figure}[t]
\centering
\begin{minipage}[t]{\textwidth}
\vspace{0pt}
\centering
% \footnotesize
\begin{tabular}[t]{L{29em} M{7em}}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{minipage}\\\vspace{2em}
\begin{minipage}[t]{\textwidth}
\vspace{0pt}
\centering
        \includegraphics[width=0.8\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
        \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}
    \label{fig:SSBM_spectral_experiments}
\end{minipage}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\begin{minipage}[t]{0.48\textwidth}
\vspace{0pt}
\centering
% \footnotesize
\begin{tabular}[t]{L{9em} M{7em}}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{minipage}\\\vspace{2em}
\begin{minipage}[t]{0.48\textwidth}
\vspace{0pt}
\centering
        \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
        \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}.}
    \label{fig:SSBM_spectral_experiments}
\end{minipage}
\end{figure}
